---
title: "Data Visualization Chapter 3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(gapminder)
library(ggplot2)
library(here)
# gapminder
p <- ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp))
p + geom_point()
p + geom_smooth()
p + geom_point() + geom_smooth()
p + geom_point() + geom_smooth(method = "lm")
p + geom_point() + geom_smooth(method = "gam") + scale_x_log10()
p + geom_point() + geom_smooth(method = "gam") + scale_x_log10(labels = scales::dollar)
p + geom_point(color = "purple") + geom_smooth(method = "loess") + scale_x_log10()
p + geom_point(alpha = 0.3) + geom_smooth(color = "orange", se = FALSE, size = 8, method = "lm") + scale_x_log10()
# se = standard error
p + geom_point(alpha = 0.3) + geom_smooth(method = "gam") + scale_x_log10(labels = scales::dollar) +
  labs(x = "GDP Per Capita", y = "Life Expectancy in Years", title = "Economic Growth and Life Expectancy", 
       subtitle = "Data points are country-years",
       caption = "Source: Gapminder.")
p <- ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp, color = continent, fill = continent))
p + geom_point() + geom_smooth(method = "loess") + scale_x_log10()

p <- ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp))
p + geom_point(mapping = aes(color = log(pop))) + scale_x_log10()
p.out <- p + geom_point() + geom_smooth(method = "loess") + scale_x_log10()
ggsave(here("figures","lifeexp_vs_gdp_gradient.png"), plot = p.out)

```

## Including Plots

You can also embed plots, for example:


 ```{r pressure, echo=FALSE}
 plot(pressure)
 ```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
